\section*{参考文献}

\begin{enumerate}[leftmargin=2em,itemsep=2pt]

\item CISO Compliance Assessment Agent. \url{https://github.com/IBM/itbench-ciso-caa-agent?tab=readme-ov-file}, a. Accessed: 2025-01-30.

\item CISO Compliance Assessment Agent. \url{https://github.com/IBM/itbench-sample-scenarios/tree/main/ciso}, b. Accessed: 2025-01-30.

\item Ansible. \url{https://www.redhat.com/en/technologies/management/ansible}, a. Accessed: 2025-01-30.

\item OPA Gatekeeper. \url{https://kubernetes.io/blog/2019/08/06/opa-gatekeeper-policy-and-governance-for-kubernetes/}, b. Accessed: 2025-01-30.

\item Kyverno, Policy as Code, Simplified! \url{https://kyverno.io}, c. Accessed: 2025-01-30.

\item Open Policy Agent. \url{https://github.com/open-policy-agent/opa}, d. Accessed: 2025-01-30.

\item NIST Cybersecurity Framework 2.0 Quick-Start Guide for Creating and Using Organizational Profiles. \url{https://www.nist.gov/cyberframework}. Accessed: 2025-01-30.

\item Crew ai. \url{https://www.crewai.com/}. Accessed: 2025-01-30.

\item Datadog. \url{https://www.datadoghq.com/}. Accessed: 2024-11-30.

\item Dynatrace. \url{https://www.dynatrace.com/}. Accessed: 2024-11-30.

\item Grafana. \url{https://grafana.com}. Accessed: 2025-01-30.

\item Instana. \url{https://www.ibm.com/products/instana}. Accessed: 2024-11-30.

\item Jaeger. \url{https://www.jaegertracing.io/}. Accessed: 2025-01-30.

\item Kubernetes. \url{https://kubernetes.io/}. Accessed: 2025-01-30.

\item Grafana Loki. \url{https://github.com/grafana/loki}. Accessed: 2025-01-30.

\item Prometheus. \url{https://prometheus.io/}. Accessed: 2025-01-30.

\item T. Ahmed, S. Ghosh, C. Bansal, T. Zimmermann, X. Zhang, and S. Rajmohan. Recommending root-cause and mitigation steps for cloud incidents using large language models. In \textit{2023 IEEE/ACM 45th International Conference on Software Engineering (ICSE)}, pages 1737--1749, 2023a. doi: 10.1109/ICSE48619.2023.00149.

\item T. Ahmed, S. Ghosh, C. Bansal, T. Zimmermann, X. Zhang, and S. Rajmohan. Recommending root-cause and mitigation steps for cloud incidents using large language models. In \textit{2023 IEEE/ACM 45th International Conference on Software Engineering (ICSE)}, pages 1737--1749, 2023b. IEEE, 2023b.

\item B. Arzani, S. Ciraci, B. T. Loo, A. Schuster, and G. Outhred. Taking the blame game out of data centers operations with netpoirot. In \textit{Proceedings of the 2016 ACM SIGCOMM Conference}, pages 440--453, 2016.

\item S. Ashok, V. Harsh, B. Godfrey, R. Mittal, S. Parthasarathy, and L. Shwartz. Traceweaver: Distributed request tracing for microservices without application modification. In \textit{Proceedings of the ACM SIGCOMM 2024 Conference}, pages 828--842, 2024.

\item A. Avizienis, J.-C. Laprie, and B. Randell. Basic Concepts and Taxonomy of Dependable and Secure Computing. \textit{IEEE Transactions on Dependable and Secure Computing (TDSC)}, 1(1):1--23, Jan. 2004.

\item F. Bagehorn, J. Rios, S. Jha, R. Filepp, L. Shwartz, N. Abe, and X. Yang. A fault injection platform for learning aiops models. In \textit{Proceedings of the 37th IEEE/ACM International Conference on Automated Software Engineering}, pages 1--5, 2022.

\item L. A. Barroso, U. H\"olzle, and P. Ranganathan. \textit{The Datacenter as a Computer: Designing Warehouse-Scale Machines}. Morgan and Claypool Publishers, 3 edition, 2018.

\item B. Beyer, N. R. Murphy, D. K. Rensin, K. Kawahara, and S. Thorne. \textit{Site Reliability Workbook: Practical Ways to Implement SRE}. O'Reilly Media, Aug. 2018.

\item B. Bogin, K. Yang, S. Gupta, K. Richardson, E. Bransom, P. Clark, A. Sabharwal, and T. Khot. Super: Evaluating agents on setting up and executing tasks from research repositories. \textit{ArXiv}, abs/2409.07440, 2024.

\item L. Boisvert, M. Thakkar, M. Gasse, M. Caccia, T. L. S. D. Chezelles, Q. Cappart, N. Chapados, A. Lacoste, and A. Drouin. Workarena++: Towards compositional planning and reasoning-based common knowledge work tasks, 2024.

\item C. Boulton. Rising cloud costs leave CIOs seeking ways to cope. \url{https://www.cio.com/article/3496509/rising-cloud-costs-leave-cios-seeking-ways-to-cope.html}. Accessed: 2025-01-30.

\item K. Budhathoki, L. Minorics, P. Bl\"obaum, and D. Janzing. Causal structure-based root cause analysis of outliers. In \textit{International Conference on Machine Learning}, pages 2357--2369. PMLR, 2022.

\item B. Burns, B. Grant, D. Oppenheimer, E. Brewer, and J. Wilkes. Borg, Omega, and Kubernetes. \textit{Communications of the ACM}, 59(5):50--57, May 2016.

\item S. Chakraborty, S. Garg, S. Agarwal, A. Chauhan, and S. K. Saini. Causil: Causal graph for instance level microservice data. In \textit{Proceedings of the ACM Web Conference 2023}, pages 2905--2915, 2023.

\item M. Chen, J. Tworek, H. Jun, Q. Yuan, H. P. de Oliveira Pinto, and J. K. et. al. Evaluating large language models trained on code, 2021.

\item Y. Chen, H. Xie, M. Ma, Y. Kang, X. Gao, L. Shi, Y. Cao, X. Gao, H. Fan, M. Wen, et al. Empowering practical root cause analysis by large language models for cloud incidents. \textit{arXiv preprint arXiv:2305.15778}, 2023.

\item Y. Chen, M. Shetty, G. Somashekar, M. Ma, Y. Simmhan, J. Mace, C. Bansal, R. Wang, and S. Rajmohan. Aiopslab: A holistic framework for evaluating ai agents for enabling autonomous cloud. November 2024a.

\item Y. Chen, H. Xie, M. Ma, Y. Kang, X. Gao, L. Shi, Y. Cao, X. Gao, H. Fan, M. Wen, J. Zeng, S. Ghosh, X. Zhang, C. Zhang, Q. Lin, S. Rajmohan, D. Zhang, and T. Xu. Automatic Root Cause Analysis via Large Language Models for Cloud Incidents. In \textit{Proceedings of the 19th European Conference on Computer Systems (EuroSys'24)}, Apr. 2024b.

\item Y. Chen, H. Xie, M. Ma, Y. Kang, X. Gao, L. Shi, Y. Cao, X. Gao, H. Fan, M. Wen, et al. Automatic root cause analysis via large language models for cloud incidents. In \textit{Proceedings of the Nineteenth European Conference on Computer Systems}, pages 674--688, 2024c.

\item CIS. Center for Internet Security Benchmarks List. \url{https://www.cisecurity.org/cis-benchmarks}, 2024. Accessed: 2025-01-30.

\item O. Community. Opentelemetry astronomy shop demo. \url{https://opentelemetry.io/docs/demo/}, 2024. Accessed: 2025-01-30.

\item J. Dean. Designs, Lessons and Advice from Building Large Distributed Systems. In \textit{Proceedings of the the 3rd Large Scale Distributed Systems and Middleware (LADIS'09)}, Oct. 2009.

\item C. Di Martino, F. Baccanico, J. Fullop, W. Kramer, Z. Kalbarczyk, and R. Iyer. Lessons Learned From the Analysis of System Failures at Petascale: The Case of Blue Waters. In \textit{Proceedings of the 44th Annual IEEE/IFIP International Conference on Dependable Systems and Networks (DSN'14)}, 2014.

\item Y. Diao, D. Horn, A. Kipf, O. Shchur, I. Benito, W. Dong, D. Pagano, P. Pfeil, V. Nathan, M. Narayanaswamy, and T. Kraska. Forecasting algorithms for intelligent resource scaling: An experimental analysis. In \textit{Proceedings of the 2024 ACM Symposium on Cloud Computing}, pages 126--143, 2024.

\item D. Donoho. Comments on Michael Jordan's essay ``the AI revolution hasn't happened yet''. \textit{Harvard Data Science Review}, June 2019.

\item A. Drouin, M. Gasse, M. Caccia, I. H. Laradji, M. D. Verme, T. Marty, L. Boisvert, Q. Cappart, D. Vazquez, N. Chapados, and A. Lacoste. Workarena: How capable are web agents at solving common knowledge work tasks?, 2024.

\item H. Fang, T. Tao, and C. Zhai. Diagnostic evaluation of information retrieval models. \textit{ACM Transactions on Information Systems (TOIS)}, 29(2):1--42, 2011.

\item Y. Fangkai, L. Wang, Z. Xu, J. Zhang, L. Li, B. Qiao, C. Couturier, C. Bansal, S. Ram, Z. Ma, I. Goiri, E. Cortez, T. Yang, V. Ruehle, S. Rajmohan, Q. Lin, and D. Zhang. Snape: Reliable and low-cost computing with mixture of spot and on-demand vms. In \textit{Proceedings of the International Conference on Architectural Support for Programming Languages and Operating Systems, Volume 3}, pages 631--643, 2023.

\item B. Feng, Z. Ding, and C. Jiang. Fast: A forecasting model with adaptive sliding window and time locality integration for dynamic cloud workloads. In \textit{IEEE Transactions on Services Computing}, pages 1184--1197, 2023.

\item R. Fonseca, G. Porter, R. H. Katz, and S. Shenker. \{X-Trace\}: A pervasive network tracing framework. In \textit{4th USENIX Symposium on Networked Systems Design \& Implementation (NSDI 07)}, 2007.

\item C. for Internet Security (CIS). \textit{CIS Benchmarks}. Center for Internet Security, 2024. Technical guidelines for secure system configurations.

\item D. Ford, F. Labelle, F. I. Popovici, M. Stokely, V.-A. Truong, L. Barroso, C. Grimes, and S. Quinlan. Availability in Globally Distributed Storage Systems. In \textit{Proceedings of the 9th USENIX Conference on Operating Systems Design and Implementation (OSDI'10)}, Oct. 2010.

\item F. Foundation. Finops data reports. \url{https://data.finops.org}, 2024a. Accessed: 2024-12-11.

\item F. Foundation. Key priorities shift in 2024. \url{https://www.finops.org/insights/key-priorities-shift-in-2024/}, 2024b. Accessed: 2024-12-11.

\item F. Foundation. Using efficiency metrics to evaluate cloud optimization and value between parts of the organization or against industry peers to inform decision-making and align finops with business objectives. \url{https://www.finops.org/framework/capabilities/benchmarking/}, 2025a. Accessed: 2025-01-30.

\item F. Foundation. Finops kpis. \url{https://www.finops.org/wg/finops-kpis/}, 2025b. Accessed: 2025-01-30.

\item M. Fuller. State of FinOps '24: Top priorities shift to reducing waste and managing commitments. \url{https://www.finops.org/insights/key-priorities-shift-in-2024/}, 2024.

\item J. Gao, N. Yaseen, R. MacDavid, F. V. Frujeri, V. Liu, R. Bianchini, R. Aditya, X. Wang, H. Lee, D. Maltz, et al. Scouts: Improving the diagnosis process through domain-customized incident routing. In \textit{Proceedings of the Annual conference of the ACM Special Interest Group on Data Communication on the applications, technologies, architectures, and protocols for computer communication}, pages 253--269, 2020.

\item S. Ghosh, M. Shetty, C. Bansal, and S. Nath. How to fight production incidents?: an empirical study on a large-scale cloud service. In \textit{Proceedings of the 13th Symposium on Cloud Computing (SoCC'22)}, Nov. 2022.

\item H. S. Gunawi, M. Hao, T. Leesatapornwongsa, T. Patana-anake, T. Do, J. Adityatama, K. J. Eliazar, A. Laksono, J. F. Lukman, V. Martin, and A. D. Satria. What bugs live in the cloud? a study of 3000+ issues in cloud systems. In \textit{Proceedings of the 5th ACM Symposium on Cloud Computing (SoCC'14)}, Nov. 2014.

\item H. S. Gunawi, M. Hao, R. O. Suminto, A. Laksono, A. D. Satria, J. Adityatama, and K. J. Eliazar. Why Does the Cloud Stop Computing? Lessons from Hundreds of Service Outages. In \textit{Proceedings of the 7th ACM Symposium on Cloud Computing (SoCC'16)}, Oct. 2016.

\item H. S. Gunawi, R. O. Suminto, R. Sears, C. Golliher, S. Sundararaman, X. Lin, T. Emami, W. Sheng, N. Bidokhti, C. McCaffrey, G. Grider, P. M. Fields, K. Harms, R. B. Ross, A. Jacobson, R. Ricci, K. Webb, P. Alvaro, H. B. Runesha, M. Hao, and H. Li. Fail-Slow at Scale: Evidence of Hardware Performance Faults in Large Production Systems. In \textit{Proceedings of the 16th USENIX Conference on File and Storage Technologies (FAST'18)}, Feb. 2018.

\item C. Guo, L. Yuan, D. Xiang, Y. Dang, R. Huang, D. Maltz, Z. Liu, V. Wang, B. Pang, H. Chen, Z.-W. Lin, and V. Kurien. Pingmesh: A large-scale system for data center network latency measurement and analysis. \textit{SIGCOMM Comput. Commun. Rev.}, 45(4):139--152, Aug. 2015. ISSN 0146-4833. doi: 10.1145/2829988.2787496.

\item Harvard Business Review Research Report. Taming it complexity through effective strategies and partnerships. \url{https://hbr.org/sponsored/2022/11/taming-it-complexity-through-effective-strategies-and-partnerships}, 2022.

\item P. H. Hochschild, P. Turner, J. C. Mogul, R. Govindaraju, P. Ranganathan, D. E. Culler, and A. Vahdat. Cores that don't count. In \textit{Proceedings of the 18th Workshop on Hot Topics in Operating Systems (HotOS'21)}, June 2021.

\item J. Huang, X. Chen, S. Mishra, H. S. Zheng, A. W. Yu, X. Song, and D. Zhou. Large language models cannot self-correct reasoning yet. \textit{arXiv preprint arXiv:2310.01798}, 2023.

\item L. Huang, M. Magnusson, A. B. Muralikrishna, S. Estyak, R. Isaacs, A. Aghayev, T. Zhu, and A. Charapko. Metastable Failures in the Wild. In \textit{Proceedings of the 16th USENIX Symposium on Operating Systems Design and Implementation (OSDI'22)}, July 2022.

\item IDC. Storm clouds ahead: Missed expectations in cloud computing. \url{https://blogs.idc.com/2024/10/28/storm-clouds-ahead-missed-expectations-in-cloud-computing/}, 2024. Blog post, published on 28 October 2024.

\item A. Ikram, S. Chakraborty, S. Mitra, S. Saini, S. Bagchi, and M. Kocaoglu. Root cause analysis of failures in microservices through causal discovery. \textit{Advances in Neural Information Processing Systems}, 35:31158--31170, 2022.

\item S. Jha, S. Cui, S. S. Banerjee, T. Xu, J. Enos, M. Showerman, Z. T. Kalbarczyk, and R. K. Iyer. Live forensics for hpc systems: A case study on distributed storage systems. In \textit{SC20: International Conference for High Performance Computing, Networking, Storage and Analysis}, pages 1--16. IEEE, 2020.

\item C. E. Jimenez, J. Yang, A. Wettig, S. Yao, K. Pei, O. Press, and K. R. Narasimhan. SWE-bench: Can language models resolve real-world github issues? In \textit{The Twelfth International Conference on Learning Representations}, 2024.

\item A. S. John. Idc predicts 80\% of cios to leverage ai and automation for business agility and insights by 2028, 2024.

\item E. Jonas, J. Schleier-Smith, V. Sreekanti, C.-C. Tsai, A. Khandelwal, Q. Pu, V. Shankar, J. M. Carreira, K. Krauth, N. Yadwadkar, J. Gonzalez, R. A. Popa, I. Stoica, and D. A. Patterson. Cloud Programming Simplified: A Berkeley View on Serverless Computing. Technical Report UCB/EECS-2019-3, University of California at Berkeley, Feb. 2019.

\item S. Kapoor, B. Stroebl, Z. S. Siegel, N. Nadgir, and A. Narayanan. Ai agents that matter. \url{https://arxiv.org/abs/2407.01502}, 2024.

\item S. Kendrick. What Takes Us Down? \textit{USENIX ;login:}, 37 (5):37--45, Oct. 2012.

\item S. M. Kerner. Crowdstrike outage explained: What caused it and what's next. \url{https://www.techtarget.com/whatis/feature/Explaining-the-largest-IT-outage-in-history-and-whats-next}, 2024.

\item J. Y. Koh, R. Lo, L. Jang, V. Duvvur, M. C. Lim, P.-Y. Huang, G. Neubig, S. Zhou, R. Salakhutdinov, and D. Fried. Visualwebarena: Evaluating multimodal agents on realistic visual web tasks, 2024.

\item J. B. Leners, H. Wu, W.-L. Hung, M. K. Aguilera, and M. Walfish. Detecting failures in distributed systems with the falcon spy network. In \textit{Proceedings of the Twenty-Third ACM Symposium on Operating Systems Principles}, pages 279--294, 2011.

\item H. Liu, S. Lu, M. Musuvathi, and S. Nath. What bugs cause production cloud incidents? In \textit{Proceedings of the 16th Workshop on Hot Topics in Operating Systems (HotOS'19)}, May 2019.

\item M. Liu, L. Pan, and S. Liu. Cost optimization for cloud storage from user perspectives: Recent advances, taxonomy, and survey. \textit{ACM Computing Surveys}, 55(13s):1--37, 2023a.

\item Q. Liu and J. Paparrizos. The elephant in the room: Towards a reliable time-series anomaly detection benchmark. In \textit{NeurIPS 2024}, 2024a.

\item Q. Liu and J. Paparrizos. The elephant in the room: Towards a reliable time-series anomaly detection benchmark. In \textit{The Thirty-eight Conference on Neural Information Processing Systems Datasets and Benchmarks Track}, 2024b.

\item Z. Liu, C. Benge, and S. Jiang. Ticket-bert: Labeling incident management tickets with language models. \textit{arXiv preprint arXiv:2307.00108}, 2023b.

\item L. Ma, T. He, A. Swami, D. Towsley, K. K. Leung, and J. Lowe. Node failure localization via network tomography. In \textit{Proceedings of the 2014 Conference on Internet Measurement Conference}, pages 195--208, 2014.

\item B. Maurer. Fail at Scale: Reliability in the Face of Rapid Change. \textit{Communications of the ACM}, 58(11):44--49, Nov. 2015.

\item T. Melissaris, K. Nabar, R. Radut, S. Rehmtulla, A. Shi, S. Chandrashekar, and I. Papapanagiotou. Elastic Cloud Services: Scaling Snowflake's Control Plane. In \textit{Proceedings of the 13th ACM Symposium on Cloud Computing (SOCC'22)}, Nov. 2022.

\item Microsoft and contributors. Dowhy: A python library for causal inference. \url{https://www.pywhy.org/dowhy/v0.12/}, 2023. Version 0.12.

\item M. D. L. C. Miguel Carreon. Idc: 80

\item N. R. Murphy, B. Beyer, C. Jones, and J. Petoff. \textit{Site Reliability Engineering: Monitoring Distributed Systems}. O'Reilly Media, 2024. Accessed: 2024-11-07.

\item NIST 800-53. NIST Special Publication 800-53 Revision 5. \url{https://nvlpubs.nist.gov/nistpubs/SpecialPublications/NIST.SP.800-53r5.pdf}, 2020.

\item A. Nodari, J. Nurminen, and C. Fruhwirth. Inventory theory applied to cost optimization in cloud computing. In \textit{Proceedings of the 31st annual ACM symposium on applied computing}, pages 470--473, 2016.

\item N. OSCAL. Open security controls assessment language. \url{https://pages.nist.gov/OSCAL/}, 2024. Accessed: 2025-01-30.

\item OSCAL-compass. Oscal-compass cncf sandbox project. \url{https://github.com/oscal-compass}, 2024. Accessed: 2025-01-30.

\item P. Osypanka and P. Nawrocki. Resource usage cost optimization in cloud computing using machine learning. In \textit{IEEE Transactions on Cloud Computing}, pages 2079--2089, 2020.

\item L. Pan, M. Saxon, W. Xu, D. Nathani, X. Wang, and W. Y. Wang. Automatically correcting large language models: Surveying the landscape of diverse self-correction strategies. \textit{arXiv preprint arXiv:2308.03188}, 2023.

\item N. Papanikolaou, S. Pearson, and M. C. Mont. Towards Natural-Language Understanding and Automated Enforcement of Privacy Rules and Regulations in the Cloud: Survey and Bibliography. In \textit{Secure and Trust Computing, Data Management, and Applications}, 2011.

\item E. Parliament and the Council of the European Union. Digital operational resilience act for the financial sector and amending regulations. \url{https://eur-lex.europa.eu/EN/legal-content/summary/digital-operational-resilience-for-the-financial-sector.html}, 2024.

\item D. Patterson, A. Brown, P. Broadwell, G. Candea, M. Chen, J. Cutler, P. Enriquez, A. Fox, E. Kiciman, M. Merzbacher, D. Oppenheimer, N. Sastry, W. Tetzlaff, J. Traupman, and N. Treuhaft. Recovery-Oriented Computing (ROC): Motivation, Definition, Techniques, and Case Studies. Technical Report UCB//CSD-02-1175, University of California Berkeley, Mar. 2002.

\item L. Pham, H. Ha, and H. Zhang. Root cause analysis for microservice system based on causal inference: How far are we? In \textit{Proceedings of the 39th IEEE/ACM International Conference on Automated Software Engineering}, pages 706--715, 2024.

\item S. Pujar, L. Buratti, X. Guo, N. Dupuis, B. Lewis, S. Suneja, A. Sood, G. Nalawade, M. Jones, A. Morari, and R. Puri. Automated code generation for information technology tasks in yaml through large language models. \url{https://arxiv.org/abs/2305.02783}, 2023.

\item B. Qiao, F. Yang, C. Luo, Y. Wang, J. Li, Q. Lin, H. Zhang, M. Datta, A. Zhou, T. Moscibroda, S. Rajmohan, and D. Zhang. Intelligent container reallocation at microsoft 365. In \textit{Proceedings of the 29th ACM Joint Meeting on European Software Engineering Conference and Symposium on the Foundations of Software Engineering}, pages 1438--1443, 2021.

\item G. Quattrocchi, E. Incerto, R. Pinciroli, C. Trubiani, and L. Baresi. Autoscaling solutions for cloud applications under dynamic workloads. In \textit{IEEE Transactions on Services Computing}, pages 804--820, 2024.

\item D. Roy, X. Zhang, R. Bhave, C. Bansal, P. Las-Casas, R. Fonseca, and S. Rajmohan. Exploring llm-based agents for root cause analysis. \url{https://arxiv.org/abs/2403.04123}, 2024.

\item G. Sahu, A. Puri, J. Rodriguez, A. Abaskohi, M. Chegini, A. Drouin, P. Taslakian, V. Zantedeschi, A. Lacoste, D. Vazquez, et al. Insightbench: Evaluating business analytics agents through multi-step insight generation. \textit{arXiv preprint arXiv:2407.06423}, 2024.

\item Salesforce. Pyrca: A python machine learning library for root cause analysis. \url{https://github.com/salesforce/PyRCA}, 2023. Version 1.0.1.

\item N. Shinn, F. Cassano, E. Berman, A. Gopinath, K. Narasimhan, and S. Yao. Reflexion: Language agents with verbal reinforcement learning, 2023.

\item B. H. Sigelman, L. A. Barroso, M. Burrows, P. Stephenson, M. Plakal, D. Beaver, S. Jaspan, and C. Shanbhag. Dapper, a large-scale distributed systems tracing infrastructure. 2010.

\item J. Storment and M. Fuller. \textit{Cloud FinOps}. O'Reilly Media, 2nd edition, 2023. Chapter 1.

\item X. Sun, R. Cheng, J. Chen, E. Ang, O. Legunsen, and T. Xu. Testing Configuration Changes in Context to Prevent Production Failures. In \textit{Proceedings of the 14th USENIX Symposium on Operating Systems Design and Implementation (OSDI'20)}, Nov. 2020.

\item C. Tan, Z. Jin, C. Guo, T. Zhang, H. Wu, K. Deng, D. Bi, and D. Xiang. \{NetBouncer\}: Active device and link failure localization in data center networks. In \textit{16th USENIX Symposium on Networked Systems Design and Implementation (NSDI 19)}, pages 599--614, 2019.

\item C. Tang, T. Kooburat, P. Venkatachalam, A. Chander, Z. Wen, A. Narayanan, P. Dowell, and R. Karl. Holistic Configuration Management at Facebook. In \textit{Proceedings of the 25th ACM Symposium on Operating System Principles (SOSP'15)}, Oct. 2015.

\item C. Tang, K. Yu, K. Veeraraghavan, J. Kaldor, S. Michelson, T. Kooburat, A. Anbudurai, M. Clark, K. Gogia, L. Cheng, B. Christensen, A. Gartrell, M. Khutornenko, S. Kulkarni, M. Pawlowski, T. Pelkonen, A. Rodrigues, R. Tibrewal, V. Venkatesan, and P. Zhang. Twine: A Unified Cluster Management System for Shared Infrastructure. In \textit{Proceedings of the 14th USENIX Conference on Operating Systems Design and Implementation (OSDI'20)}, Nov. 2020.

\item L. Tang, C. Bhandari, Y. Zhang, A. Karanika, S. Ji, I. Gupta, and T. Xu. Fail through the Cracks: Cross-System Interaction Failures in Modern Cloud Systems. In \textit{Proceedings of the 18th European Conference on Computer Systems (EuroSys'23)}, May 2023.

\item H. Tupsamudre, A. Kumar, V. Agarwal, N. Gupta, and S. Mondal. AI-Assisted Controls Change Management for Cybersecurity in the Cloud. In \textit{Thirty-Fourth Annual Conference on Innovative Applications of Artificial Intelligence (IAAI-22)}, 2022.

\item L. R. Varshney, N. S. Keskar, and R. Socher. Pre-trained AI models: Performativity, mobility, and change. arXiv:1909.03290 [cs.CY]., Sept. 2019.

\item K. Veeraraghavan, J. Meza, S. Michelson, S. Panneerselvam, A. Gyori, D. Chou, S. Margulis, D. Obenshain, S. Padmanabha, A. Shah, Y. J. Song, and T. Xu. Maelstrom: Mitigating Datacenter-level Disasters by Draining Interdependent Traffic Safely and Efficiently. In \textit{Proceedings of the 13th USENIX Symposium on Operating Systems Design and Implementation (OSDI'18)}, Oct. 2018.

\item Q. Wang, J. Rios, S. Jha, K. Shanmugam, F. Bagehorn, X. Yang, R. Filepp, N. Abe, and L. Shwartz. Fault injection based interventional causal learning for distributed applications. In \textit{Proceedings of the AAAI Conference on Artificial Intelligence}, volume 37, pages 15738--15744, 2023.

\item J. Xie, K. Zhang, J. Chen, T. Zhu, R. Lou, Y. Tian, Y. Xiao, and Y. Su. Travelplanner: A benchmark for real-world planning with language agents. \url{https://arxiv.org/abs/2402.01622}, 2024a.

\item Z. Xie, Y. Zheng, L. Ottens, K. Zhang, C. Kozyrakis, and J. Mace. Cloud atlas: Efficient fault localization for cloud systems using language models and causal insight. \url{https://arxiv.org/abs/2407.08694}, 2024b.

\item B. Xu, Z. Peng, B. Lei, S. Mukherjee, Y. Liu, and D. Xu. Rewoo: Decoupling reasoning from observations for efficient augmented language models. \url{https://arxiv.org/abs/2305.18323}, 2023.

\item T. Xu, J. Zhang, P. Huang, J. Zheng, T. Sheng, D. Yuan, Y. Zhou, and S. Pasupathy. Do Not Blame Users for Misconfigurations. In \textit{Proceedings of the 24th Symposium on Operating System Principles (SOSP'13)}, Farmington, PA, Nov. 2013.

\item J. Yang, C. E. Jimenez, A. Wettig, K. Lieret, S. Yao, K. Narasimhan, and O. Press. Swe-agent: Agent-computer interfaces enable automated software engineering. \textit{arXiv preprint arXiv:2405.15793}, 2024a.

\item X. Yang, R. Arora, S. Jha, C. Narayanaswami, C. Lam, J. Leichter, Y. Deng, and D. Sow. Optimizing it finops and sustainability through unsupervised workload characterization. In \textit{Proceedings of the AAAI Conference on Artificial Intelligence.}, pages 22990--22996, 2024b.

\item S. Yao, J. Zhao, D. Yu, N. Du, I. Shafran, K. R. Narasimhan, and Y. Cao. React: Synergizing reasoning and acting in language models. In \textit{The Eleventh International Conference on Learning Representations}, 2023.

\item Z. Yao, C. Pei, W. Chen, H. Wang, L. Su, H. Jiang, Z. Xie, X. Nie, and D. Pei. Chain-of-event: Interpretable root cause analysis for microservices through automatically learning weighted event causal graph. In \textit{Companion Proceedings of the 32nd ACM International Conference on the Foundations of Software Engineering}, pages 50--61, 2024.

\item A. Yehoshua, I. Kolchinsky, and A. Schuster. Cco - cloud cost optimizer. In \textit{Proceedings of the 16th ACM International Conference on Systems and Storage}, pages 137--137, 2023.

\item X. Zhang, T. Mittal, C. Bansal, R. Wang, M. Ma, Z. Ren, H. Huang, and S. Rajmohan. Flash: A workflow automation agent for diagnosing recurring incidents. October 2024.

\item L. Zheng, W.-L. Chiang, Y. Sheng, S. Zhuang, Z. Wu, Y. Zhuang, Z. Lin, Z. Li, D. Li, E. P. Xing, H. Zhang, J. E. Gonzalez, and I. Stoica. Judging llm-as-a-judge with mt-bench and chatbot arena. \url{https://arxiv.org/abs/2306.05685}, 2023.

\item X. Zhou, X. Peng, T. Xie, J. Sun, C. Ji, W. Li, and D. Ding. Fault analysis and debugging of microservice systems: Industrial survey, benchmark system, and empirical study. \textit{IEEE Transactions on Software Engineering}, 47(2):243--260, 2018.

\item Z. Zhu, C. Lee, X. Tang, and P. He. Hemirca: Fine-grained root cause analysis for microservices with heterogeneous data sources. \textit{ACM Transactions on Software Engineering and Methodology}, 33(8):1--25, 2024.

\end{enumerate}
